---
title: "Cycles and Forecasting of Hawaiin Hotel Occupancy Presentation"
author: "Ran Jin"
date: "4/13/2018"
output:
  beamer_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(astsa)
require(quantmod)
require(timeSeries)
require(knitr)
require(forecast)
require(tseries)
```

## Background and Key Question

Understanding the dynamics and forecasting the Hawaiin hotel room occupancy is essential to better control a budget for a trip. 

Key Questions:

- Is there a predominant cycle present in the Hawaiian hotel occupancy rate change? 

- What are the forecast, and forecast error bounds for the Hawaiin hotel occupany rate change for the next 3 years?

To better address these questions, a time series model will be developed. In addition, since it is a quarterly data, I will also develop a model based spectral density estimate, which will address possible cycles in the data. 

## Data: Definition, Aquisition and Exploration

I am using the Quarterly Hawaiian hotel occupancy rate change from 1982-I to 2015-IV from the *astsa* package. It is defined as a ts object. 

##Plot1
```{r}
dhor<-diff(hor)
ts.plot(dhor, main="Quarterly Hawaiian hotel occupancy rate change")

```

##Plot2
```{r}
seasonplot(dhor)
```

## ACF and PACF 
```{r}
invisible(astsa::acf2(dhor,40))
```

## Modeling Recruitment
```{r}
recfit0<-invisible(astsa::sarima(dhor,p=4,d=0,q=0,
                                 no.constant=FALSE, 
                                 details=F))
recfit1<-invisible(astsa::sarima(dhor,p=4,d=0,q=1,
                                 no.constant=FALSE, 
                                 details=F))
recfit2<-invisible(astsa::sarima(dhor,p=4,d=0,q=2,
                                 no.constant=FALSE, 
                                 details=F))
recfit3<-invisible(astsa::sarima(dhor,p=4,d=0,q=3,
                                 no.constant=FALSE, 
                                 details=F))
recfit4<-invisible(astsa::sarima(dhor,p=4,d=0,q=4,
                                 no.constant=FALSE, 
                                 details=F))
```

## Comparison
ARIMA(4,0,4) is the best model here.
```{r}
BIC<-c(recfit0$BIC,recfit1$BIC,recfit2$BIC,
       recfit3$BIC,recfit4$BIC)
AIC<-c(recfit0$AIC,recfit1$AIC,recfit2$AIC,
       recfit3$AIC,recfit4$AIC)
chart<-cbind(BIC,AIC)
rownames(chart) <- c('ARIMA(4,0,0)','ARIMA(4,0,1)',
                     'ARIMA(4,0,2)','ARIMA(4,0,3)',
                     'ARIMA(4,0,4)')
as.table(chart)
```

## With seasonal Component
```{r}
recfitar<-invisible(astsa::sarima(dhor,p=4,d=0,q=4,
                                  P=1,S=4,no.constant=F,
                                  details=F))
recfitma<-invisible(astsa::sarima(dhor,p=4,d=0,q=4,
                                  S=4,Q=1,no.constant=F,
                                  details=F))
recfit11<-invisible(astsa::sarima(dhor,p=4,d=0,q=4,
                                  P=1,S=4,Q=1,
                                  no.constant=FALSE,
                                  details=F))
```

## Comparison
ARIMA(4,0,4)xAR(1)[4] is the best fitted model here.
```{r}
BIC<-c(recfitar$BIC,recfitma$BIC,recfit11$BIC)
AIC<-c(recfitar$AIC,recfitma$AIC,recfit11$AIC)
AICc<-c(recfitar$AICc,recfitma$AICc,recfit11$AICc)
chart<-cbind(BIC,AIC)
chart<-cbind(chart,AICc)
rownames(chart) <- c('ARIMA(4,0,4)xAR(1)[4]',
                     'ARIMA(4,0,4)xMA(1)[4]',
                     'ARIMA(4,0,2)xARMA(1,1)[4]')
as.table(chart)
```

## Model Estimation
```{r}
kable(recfitar$ttable, caption=
        "SARIMA(4,0,4)x(1,0,0)[4] Parameter Estimates")
```

## What is the predominant period?

```{r}
sa <- spec.pgram(dhor,log='no')
text(frequency(dhor)*0.45, 600, substitute(omega==1/2))
```

## Forecasting 2016-2018

```{r}
sarima.for(dhor,n.ahead=12,p=4,d=0,q=4,P=1,S=4,Q=0)
```

## Summary Conclusions
-The temporal dynamics of the occupancy rate of Hawaiin hotels is well captured by a seasonal model ARIMA(4,0,4)xAR(1)[4].

-We also found the predominant cycle the occupancy rate change series, as indicated by the estimate of the spectral density. 

-Forecasts predict the near term behavior of the series (3 years ahead). And we see that the longterm forecasts oscillates around the estimated mean of the process, as expected. 
