---
title: "Influential Factors for NYC Housing Prices in 2015"
author: "RAN JIN, XIAO WANG, SHIBO YU, ZHUOWEI HAN (GROUP 13)"
geometry: margin=1in
output: pdf_document
fontsize: 10pt
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, tidy.opts = list(width.cutoff = 70), tidy = TRUE, fig.width = 8, fig.height = 6, warning = FALSE, message = FALSE)
#importing library
library(ggplot2)
library(RSQLite)
library(DBI)
library(sqldf)
library(RSQLite)
library(ggplot2)
library(faraway)
library(grid)
library(gridBase)

```
#**1 Introduction**:  

  Housing prices in NYC vary in a wide range in different five boroughs. So except the obvious factors such as the different functions that these boroughs are assigned, does there exist some other incredible factors that could potentially influence the housing prices, even though they seem to be unrelated to the real estate market at all? More specifically, for consumers, what factors are essential to consider while buying a house in NYC? We choose the numbers of death and injury caused by car collisions, the total GHG emissions and the total number of trees as factors to represent safety, pollution level, and vegetation coverages, repsectively in these five boroughs. By analyzing thoroughly these three datasets (including Total Number of Trees in 2015[1], Numbers of Deaths And Injuries Caused By Car Collision in 2015[2] adn Total Greenhouse Gas (GHG) Emission in 2013[3]), we are trying to find out if there exists some correlations between the housing price in every borough and these factors. And finally, we will construct 5 linear regression models using these three datasets and housing price in each borough in 2015[4] to complete our analysis.

### Our questions are:

* What is the hypothesis we can derive from direct/indirect GHH emission in each borough? 
* What is the hypothesis we can derive from pedetrians killed, cyclists killed, and motorists killed from car collision in each borough? 
* What is the hypothesis we can derive from pedetrians injured, cyclists injured, and motorists injured from car collision in each borough? 
* Whether or not that the housing price can be affected by the trees distribution of 5 boroughs in New York City. If the answer is YES, how would the relationship be? Is it linear relationship or can be transform into linear relationship?
* Can we fit good linear models of NYC housing prices in these 5 boroughs regressing on some or all of the variables within the datasets we display later on in the report? If so, how are the housing price in each borough linked to the factors? (Positive correlation or negative.)

  And the followings are our analysis and interpretations.




#**2 The Database Table**: 


```{r p3, echo=FALSE,results='asis'}
##plotting a table explaining datasets used in the report
matrixtotal<-matrix(c("nychousing","tree","database","energy","The information of houses that were sold in 2015 in New York","the information of all the trees in New York in 2015","The information of car collision in New York in 2015","The information about inspected GHG in New York in 2013"),nrow = 4)
colnames(matrixtotal) <- c("table","Description")
rownames(matrixtotal) <- 1:4
matrixtotal <- as.table(matrixtotal)
knitr::kable(matrixtotal)
```

    






```{r, echo=FALSE,warning=FALSE,message=FALSE}
#import database
dcon <- dbConnect(SQLite(), dbname = "/Users/air/Desktop/project605.db")

#creating new tables in SQL
#grouping by zip codes  to sum of persons killed and sum of persons injured which are our beta 1, and 2. 
query <- paste0("
                CREATE TEMPORARY TABLE nyctokill AS
                SELECT  ZIPCODE, sum(PERSONSKILLED) AS pk, sum(PERSONSINJURED) AS pj
                FROM database
                GROUP BY ZIPCODE;")
res <- dbSendQuery(dcon, query)
data <- dbFetch(res, -1)
dbClearResult(res)

#grouping by zip codes  to mean of sale prices of housing which are our y-values
query1 <- paste0("
                CREATE TEMPORARY TABLE nycsale AS
                SELECT  ZIPCODE, avg(SALEPRICE) AS sp
                FROM nychousing
                GROUP BY ZIPCODE;")
res1 <- dbSendQuery(dcon, query1)
data1 <- dbFetch(res1, -1)
dbClearResult(res1)

#grouping by zip codes  to sum of trees which is our beta 3. 
query2 <- paste0("
                CREATE TEMPORARY TABLE nyctotree AS
                SELECT  postcode, count(*) AS numtree, borocode, borough
                FROM tree
                GROUP BY postcode;")
res2 <- dbSendQuery(dcon, query2)
data2 <- dbFetch(res2, -1)
dbClearResult(res2)

##grouping by zip codes  to total MtCo2e Emission which is our beta 4. 
query3 <- paste0("
                CREATE TEMPORARY TABLE nyctoenergy AS
                SELECT  Postcode, sum(TotalMtCO2eEmission) AS emission
                FROM energy
                GROUP BY Postcode;")
res3 <- dbSendQuery(dcon, query3)
data3 <- dbFetch(res3, -1)
dbClearResult(res3)

#inner join
res <- dbSendQuery(conn = dcon, "
SELECT a.ZIPCODE, a.sp,
       b.pk, b.pj,
       c.numtree, c.borocode, c.borough,
       d.emission
FROM nycsale AS a
INNER JOIN nyctokill AS b
ON a.ZIPCODE = b.ZIPCODE
INNER JOIN nyctotree AS c
ON a.ZIPCODE = c.postcode
INNER JOIN nyctoenergy AS d
ON a.ZIPCODE = d.Postcode
ORDER BY a.ZIPCODE;
")
newtable<-dbFetch(res, -1)
```







#**3 Analysis**:


```{r results = FALSE}
##plotting a graph of GHG emission in different boroughs
emission <- read.csv(file = "/Users/air/Desktop/emission.csv", header = TRUE, sep = ",")

head(emission)

n <- nrow(emission)

emissionTransform <- data.frame(rep(x = emission$Borough, times = 2), rep(x = emission$Postcode, times = 2), c(rep(x = "direct", times = n), rep(x = "indirect", times = n)), c(emission$direct, emission$indirect))

dim(emissionTransform)

colnames(emissionTransform) <- c("Borough", "Postcode", "Type", "Emission")


par(mar = c(3, 5, 1.5, 1), oma = c(0, 0, 0, 0), mgp = c(1, 0.1, 0), cex = 1, tcl = -0.25, lwd = 1.25)

ggplot(data = emissionTransform, mapping = aes(x = reorder(x = Borough, X = -Emission, FUN = sum), y = Emission / 1e8, fill = Type, order = Emission)) + 
    geom_bar(stat = "identity", position = "stack") + 
    scale_x_discrete(name = "Borough") + 
    scale_y_continuous(name = "log(Emission) (x 1e8)") + 
    scale_fill_hue("Emission Type", labels = c("Direct", "Indirect")) + 
    theme_classic()+ ggtitle("Emission of direct and indirect GHG in five boroughs")
```

* The number of indirect emission in Broolyn and Manhattan seems way much bigger than
that of direct emssion.   
* From the graph above, we may guess the housing price in Broolyn and Manhattan may be lower than other places due to the GHG.   




















```{r, echo=FALSE, message=FALSE,warning=FALSE, fig.height=10}
##graphing numbers of people died from car collision in different boroughs
query <- paste0("
                SELECT BOROUGH, sum(PEDESTRIANSKILLED) AS PEDESTRIANSKILLED, sum(CYCLISTSKILLED) AS CYCLISTSKILLED, sum(MOTORISTSKILLED) AS MOTORISTSKILLED
                FROM database
                GROUP BY BOROUGH;")
res <- dbSendQuery(dcon, query)
data <- dbFetch(res, -1)
dbClearResult(res)
datan<- data[-1,]
par(mfrow=c(1,3))
barplot(datan$PEDESTRIANSKILLED, main="pedestrians killed", horiz=TRUE, names.arg = c("BRONX", "BROOKLYN", "MANHATTAN","QUEENS","STATEN ISLAND"),cex.names = 1,col = 'red',xlim = c(0,70))
barplot(datan$CYCLISTSKILLED, main="cyclists killed", horiz=TRUE, names.arg = c("BRONX", "BROOKLYN", "MANHATTAN","QUEENS","STATEN ISLAND"),cex.names = 1,col = 'red', xlim = c(0,70))
barplot(datan$MOTORISTSKILLED, main="motorists killed", horiz=TRUE, names.arg = c("BRONX", "BROOKLYN", "MANHATTAN","QUEENS","STATEN ISLAND"),cex.names = 1,col = 'red',xlim = c(0,70))
```

* The 3 graphs above represent the numbers of pedestrians killed, cyclists killed, motorists killed respectively from car collisions for each borough.   

* Pedestrians killed have a significantly larger number than the other two.   

* Brooklyn and Queens appear to have the relatively higher numbers of incidents which might drive the housing prices in those two areas down.   

```{r setup2, echo=FALSE, message=FALSE,warning=FALSE, fig.height=10}
##graphing numbers of people injured car collision in different boroughs
query1 <- paste0("
                SELECT BOROUGH, sum(PEDESTRIANSINJURED) AS PEDESTRIANSINJURED, sum(CYCLISTSINJURED) AS CYCLISTSINJURED, sum(MOTORISTSINJURED) AS MOTORISTSINJURED
                FROM database
                GROUP BY BOROUGH;")
res1 <- dbSendQuery(dcon, query1)
dataa <- dbFetch(res1, -1)
dbClearResult(res1)
dataa1<- dataa[-1,]
par(mfrow=c(1,3))
barplot(dataa1$PEDESTRIANSINJURED, main="pedestrians injured", horiz=TRUE, names.arg = c("BRONX", "BROOKLYN", "MANHATTAN","QUEENS","STATEN ISLAND"),cex.names = 1,col = 'blue', xlim = c(0,20000))
barplot(dataa1$CYCLISTSINJURED, main="cyclists injured", horiz=TRUE, names.arg = c("BRONX", "BROOKLYN", "MANHATTAN","QUEENS","STATEN ISLAND"),cex.names = 1,col = 'blue',xlim = c(0,20000))
barplot(dataa1$MOTORISTSINJURED, main="motorists injured", horiz=TRUE, names.arg = c("BRONX", "BROOKLYN", "MANHATTAN","QUEENS","STATEN ISLAND"),cex.names = 1,col = 'blue',xlim = c(0,20000))
```

* The 3 graphs above represent the numbers of pedestrians injured, cyclists injured, motorists injured respectively from car collisions for each borough.    

* motorists injured have a significantly larger number than the other two.    

* Brooklyn and Queens still appear to have the relatively higher numbers of incidents which might drive the housing prices in those two areas down.     

```{r p33, echo=FALSE,results='asis'}
##creating a table explaining variables
matrixhousing<-matrix(c("borough","saleprice","tax class of time of sale","building class category","county-level administrative divisions","transaction price","the housing tax level at the time of sale","the building category at the time of construction"),nrow = 4)
colnames(matrixhousing) <- c("Variable","Description")
rownames(matrixhousing) <- 1:4
matrixhousing <- as.table(matrixhousing)
knitr::kable(matrixhousing)
```




```{r p333, echo=FALSE,warning=FALSE,message=FALSE}
##select borough,saleprice and tax class at time of sale to construct a new data frame.
res <- dbSendQuery(conn = dcon, "
SELECT BOROUGH,SALEPRICE,TAXCLASSATTIMEOFSALE
FROM nychousing
ORDER BY TAXCLASSATTIMEOFSALE;")
borough_rate <- dbFetch(res, -1)
dbClearResult(res)

borough_rate$BOROUGH<-factor(borough_rate$BOROUGH,levels = c("1","2","3","4","5"),labels = c("Mahattan","Brooklyn","Queens","The Bronx","Staten Island"))


##use the new data frame to draw a graph to show the percentage of different tax class in five boroughs
ggplot(data = borough_rate) + 
  aes(x = BOROUGH, fill = TAXCLASSATTIMEOFSALE) +
  geom_bar(position = "fill") +
  ggtitle("Percentage of different tax class in five boroughs") + scale_x_discrete(limits = rev(levels(borough_rate$BOROUGH))) + coord_flip()+theme(plot.title = element_text(hjust = 0.5,size = 22)) 
  

```

* The numbers 1,2,3,4 in the above graph represent the different tax level 19.991%, 12.892%, 10.934% and 10.574. There is no doubt that the different level of tax could show the different level of houses.    
* The percentage of the houses that should be paid the lowest tax in the five boroughs are similar.    
* The highest tax is paid most in the Staten Island.    
* In Mahattan, the ratio of highest tax is incredible low.    
* The graph gives us some hint that the house size in Mahattan may be smaller and in Staten Island, people are wealthy enough to buy some huge houses.     
* So the most busiest place may not have the highest housing price.   


```{r, fig.width=9,fig.height=5,echo=FALSE,warning=FALSE,message=FALSE}
## select 3 variables (health, borough, postcode) from dataset "tree" 
## to construct a dataframe
wxres1 <- dbSendQuery(conn = dcon, "
SELECT health, borough, postcode
FROM tree;
")
wxdf1 <- dbFetch(wxres1, -1)
dbClearResult(wxres1)

## remove rows with blanks
wxdf1 <- wxdf1[!(wxdf1$health =="" | wxdf1$borough =="" ), ]

## remove rows whose zipcode in not in NEWTABLE
wxdf1 <- wxdf1[wxdf1$postcode %in% newtable$ZIPCODE,]

## plot respective percentage of trees in different health conditions of 
## 5 boroughs in NYC

wxplot1 <- ggplot(data = wxdf1) + 
  aes(x = borough, fill = health) +
  geom_bar(position = "fill") +
  ggtitle("Percentage of trees in different health conditions")

  
## plot respective distribution of trees in different health conditions of 
## 5 boroughs in NYC
wxplot2 <- ggplot(data = wxdf1) + 
  aes(x = borough, fill = health) +
  geom_bar(position = "dodge") +
  ggtitle("Distribution of trees in different health conditions")

vp1 <- viewport(x = 0, y = 0.5, width = 1, height = 0.5,
               just = c("left", "bottom"))
print(wxplot1, vp = vp1)
vp2 <- viewport(x = 0, y = 0, width = 1, height = 0.5,
               just = c("left", "bottom"))
print(wxplot2, vp = vp2)

## select 2 variables(borough, numtree) from dataset Nyctotree and create
## a new table "wx_nyctrees" by grouping by borough
## To avoid to use "dplyr", I export "wx_nyctrees" as "csv.file" and save the
## file outside the DB brower, and then "read.csv" in "R markdown" for further 
## ggplot. This explains why I can't run the following code when finally knitting 
## to a PDF file.
## Original codes as follows with "######" ahead.
###### theme_set(theme_classic())
###### wxres2 <- dbSendQuery(conn = dcon,"
######                CREATE TABLE wx_nyctrees AS
######               SELECT  borough, sum(numtree) AS number
######                FROM nyctotree
######                GROUP BY borough;")
###### wxdf2 <- dbFetch(wxres2, -1)
###### dbClearResult(wxres2)
```

```{r}
##import data
wxdata <- read.csv("/Users/air/Desktop/wx_nyctrees_piechart.csv", header = T)
## plot pie-chart to show respective total number of trees in 5 boroughs in NYC
pie <- ggplot(wxdata, aes(x = "", y=number, fill = factor(borough))) + 
  geom_bar(width = 1, stat = "identity") +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + 
  labs(fill="borough", 
       x=NULL, 
       y=NULL, 
       title="Respective total number of trees in 5 boroughs in NYC", 
       caption="Source: dataset Tree")
pie + coord_polar(theta = "y", start=0)
par(mfrow=c(1,1))
```


* The above three plots can help us find out and easily compare the distributions of trees in the five bouroughs of New York City, which may give us some clues on how the trees distribution would affect the housing price here.     
* As seen from the 1st plot, the percentages of trees in different health conditions are almost the same for the five bouroughs.   
* The 2nd plot conveys very different information from the 1st plot because the number distribution of trees in different health conditions are quite distinct, except for "Poor" trees. Surprisingly but understandably, the most developed Manhanttan has least "Fair" trees and "Good" trees, which may be substituted with countless skyscapers.   
* The 3rd pie-chart further shows the number of trees without differentiating the health conditions. The colorful areaes shows the proportion of respect total number of trees in the five bouroughs, with the specific numbers accumulated in a clockwise direction.       









```{r echo=FALSE,warning=FALSE,message=FALSE}
## Create a table to show the variables we are interested in.
var.table <- matrix(c("zipcode", "Five-digit zipcode in New York City",
                      "sp", "Average housing saleprice in each zipcode",
                      "pk", "Number of people killed by accidents in each zipcode",
                      "pj", "Number of people injured by accidents in each zipcode",
                      "numtree", "Number of trees located in each zipcode",
                      "borough[1]", "Name of borough in New York City",
                      "borocode[2]", "Code for borough in which tree point is located",
                      "emission", "Total emission of GHG[3]"),
                    ncol=2, byrow=TRUE)
colnames(var.table) <- c("Variable","Description")
rownames(var.table) <- 1:8
var.table <- as.table(var.table)
knitr::kable(var.table)
```


### Explanation to the table
* borough: Manhattan, Bronx, Brooklyn, Queens, Staten Island.   
* borocode: 1(Manhattan), 2(Bronx), 3(Brooklyn), 4(Queens), 5(Staten Island).   
* GHG: greenhouse gases including $CO_{2}$, $CH_{4}$, and $N_{2}O$. For further information, please visit https://www.archibus.com/ai/abizfiles/v21.1_help/archibus_help/Subsystems/webc/Content/gloss/carbon_footprint/carbon_diox_equiv_def.htm.


### Interpretation of the tables

* The above table shows the variables extracted from the original four raw dataset by "INNER JOIN" all of them via their common variable "zipcode".   
* These variables would be used for our FINAL analysis on how the housing price can be influenced by other variables.    
* Given that the same variable may have varying degrees of impact on housing price in different boroughs, the above table is further divided into five sub-tables according to the five boroughs in New York.    
* Then, five independent and systematic regression analyses are performed with regard to five boroughs.    


```{r results=FALSE, echo=FALSE,warning=FALSE,message=FALSE}
##Fitting all variables into our linear regression model
f<- lm(sp~pk+pj+numtree+emission, data = newtable)
full<- lm(sp~0+pk+pj+numtree+emission, data = newtable)
plot(fitted.values(f),residuals(f), xlab = 'fitted values', ylab = 'residuals', main = 'fitted vs. res for full model')

a1<- unname(summary(f)$r.squared)
a2<- unname(summary(full)$adj.r)
a3<- unname(summary(f)$adj.r)
```

* we first fitted the full model using all four variables including total people killed, total people injured, number of trees, and the total emissions of GHG as the regressors and we found that R squared is relatively low which is `r a1`. 

* the full model also has a graph of fitted values vs. residuals of a non-constant looking variances. (heteroskedasticity)

* Since the housing price is never 0, the beta 0 intercept would be pointless. 

* Thus, we fitted the new full model using all four variables without the intercept and got a lower adjusted R squared `r a2` than the previous model with the intercept `r a3`.

```{r echo=FALSE,warning=FALSE,message=FALSE}
##Fitting three variables into our linear regression model
three<- lm(sp~0+pk+pj+numtree,data = newtable)
##Fitting two variables into our linear regression model
two<- lm(sp~0+pk+pj,data = newtable)
##Fitting one variable into our linear regression model
one<- lm(sp~0+pk,data = newtable)

b1<- unname(coefficients(full)[1])
b2<- unname(coefficients(full)[2])
b3<- unname(coefficients(full)[3])
b4<- unname(coefficients(full)[4])
b5<- unname(summary(full)$adj.r)
b6<- unname(summary(three)$adj.r)
b7<- unname(summary(two)$adj.r)
b8<- unname(summary(one)$adj.r)
```

* `r b1`, `r b2`, `r b3`, `r b4` are coefficients for pk,pj,numtree, and emission.

* `r b5`, `r b6`, `r b7`, `r b8` are adjusted R squared from full model, model with three variables, model with two variables, and model with one variable.

```{r results=FALSE, echo=FALSE,warning=FALSE,message=FALSE,fig.height=4.5}
##residuals vs. fitted plot
plot(fitted.values(full),residuals(full),ylab = 'residuals',xlab = 'fitted values', main = 'fitted vs. res')
```

* Since the fitted values vs. residuals plot does not look spreaded here. We will  use some different weights on the regressors.      

```{r results=FALSE, echo=FALSE,warning=FALSE,message=FALSE, fig.height=4.5}
##fitting new weights to the regression model and plotting the residuals vs. fitted
new<- lm(residuals(full)~pk+pj+numtree+emission,data = newtable)
wi = 1 / (fitted.values(new))^2
full1<- lm(sp~0+pk+pj+numtree+emission,data = newtable,weights = wi)
plot(sqrt(wi) * residuals(full1) ~ fitted.values(full1), pch = 19, data = newtable, xlab= 'fitted values', ylab= 'residuals', main='fitted vs. res with new weights', col = 'red')
abline(h = 0, col = 'blue')
```

* Now the fitted values vs. residuals plot looks much better than the previous one with some different weights we have applied since the points are much more spreaded. Thus, we will use the same weighting method and non-intercept linear model for the each of the regression analysis of the boroughs.    

```{r p1111111, echo=FALSE,warning=FALSE,message=FALSE, fig.height=10}
##creating new tables for each borough
table1<-newtable[newtable$borough=="Manhattan",]
table2<-newtable[newtable$borough=="Brooklyn",]
table3<-newtable[newtable$borough=="Queens",]
table4<-newtable[newtable$borough=="Bronx",]
table5<-newtable[newtable$borough=="Staten Island",]
```

```{r p12, echo=FALSE,warning=FALSE,message=FALSE, fig.height=4.5}
##linear regression on all four variables with weights in Manhattan
full1<- lm(sp~0+pk+pj+numtree+emission,data = table1)
new1<- lm(residuals(full1)~pk+pj+numtree+emission,data = table1)
wi1 = 1 / (fitted.values(new1))^2
full1<- lm(sp~0+pk+pj+numtree+emission,data = table1,weights = wi1)
plot(sqrt(wi1) * residuals(full1) ~ fitted.values(full1), pch = 19, data = table1, main="residuals vs fitted value in Manhattan",xlab="fitted value",ylab = "residuals")
abline(h = 0)

c1<-unname(full1$coefficients[1])
c2<-unname(full1$coefficients[2])
c3<-unname(full1$coefficients[3])
c4<-unname(full1$coefficients[4])
c5<-unname(summary(full1)$r.squared)
```

* `r c1`, `r c2`, `r c3`, `r c4` are the coefficients for pk, pj, numtree, and emission respectively.
* `r c5` is the R squared for the new full model in Manhattan.


```{r p2, echo=FALSE,warning=FALSE,message=FALSE, fig.height=4.5}
##linear regression on all four variables with weights in Brooklyn
full2<- lm(sp~0+pk+pj+numtree+emission,data = table2)
new2<- lm(residuals(full2)~pk+pj+numtree+emission,data = table2)
wi2 = 1 / (fitted.values(new2))^2
full2<- lm(sp~0+pk+pj+numtree+emission,data = table2,weights = wi2)
plot(sqrt(wi2) * residuals(full2) ~ fitted.values(full2), pch = 19, data = table2, main="residuals vs fitted value in Brooklyn",xlab="fitted value",ylab = "residuals")
abline(h = 0)

d1<- unname(full2$coefficients[1])
d2<- unname(full2$coefficients[2])
d3<- unname(full2$coefficients[3])
d4<- unname(full2$coefficients[4])
d5<- unname(summary(full2)$r.squared)

```

* `r d1`, `r d2`, `r d3`, `r d4` are the coefficients for pk, pj, numtree, and emission respectively.   
* `r d5` is the R squared for the new full model in Brooklyn.

```{r p333333333, echo=FALSE,warning=FALSE,message=FALSE, fig.height=4.5}
##linear regression on all four variables with weights in Queens
full3<- lm(sp~0+pk+pj+numtree+emission,data = table3)
new3<- lm(residuals(full3)~pk+pj+numtree+emission,data = table3)
wi3 = 1 / (fitted.values(new3))^2
full3<- lm(sp~0+pk+pj+numtree+emission,data = table3,weights = wi3)
plot(sqrt(wi3) * residuals(full3) ~ fitted.values(full3), pch = 19, data = table3, main="residuals vs fitted value in Queens",xlab="fitted value",ylab = "residuals")
abline(h = 0)

e1<- unname(full3$coefficients[1])
e2<- unname(full3$coefficients[2])
e3<- unname(full3$coefficients[3])
e4<- unname(full3$coefficients[4])
e5<- unname(summary(full3)$r.squared)

```

* `r e1`, `r e2`, `r e3`, `r e4` are the coefficients for pk, pj, numtree, and emission respectively.   
* `r e5` is the R squared for the new full model in Queens.


```{r p4, echo=FALSE,warning=FALSE,message=FALSE, fig.height=4.5}
##linear regression on all four variables with weights in Bronx
full4<- lm(sp~0+pk+pj+numtree+emission,data = table4)
new4<- lm(residuals(full4)~pk+pj+numtree+emission,data = table4)
wi4 = 1 / (fitted.values(new4))^2
full4<- lm(sp~0+pk+pj+numtree+emission,data = table4,weights = wi4)
plot(sqrt(wi4) * residuals(full4) ~ fitted.values(full4), pch = 19, data = table4, main="residuals vs fitted value in Bronx",xlab="fitted value",ylab = "residuals")
abline(h = 0)


f1<- unname(full4$coefficients[1])
f2<- unname(full4$coefficients[2])
f3<- unname(full4$coefficients[3])
f4<- unname(full4$coefficients[4])
f5<- unname(summary(full4)$r.squared)
```

* `r f1`, `r f2`, `r f3`, `r f4` are the coefficients for pk, pj, numtree, and emission respectively.   
* `r f5` is the R squared for the new full model in Bronx.

```{r p5, echo=FALSE,warning=FALSE,message=FALSE, fig.height=4.5}
##linear regression on all four variables with weights in Staten Island
full5<- lm(sp~0+pk+pj+numtree+emission,data = table5)
new5<- lm(residuals(full5)~pk+pj+numtree+emission,data = table5)
wi5 = 1 / (fitted.values(new5))^2
full5<- lm(sp~0+pk+pj+numtree+emission,data = table5,weights = wi5)
plot(sqrt(wi5) * residuals(full5) ~ fitted.values(full5), pch = 19, data = table5, main="residuals vs fitted value in Staten Island",xlab="fitted value",ylab = "residuals")
abline(h = 0)

g1<- unname(full5$coefficients[1])
g2<- unname(full5$coefficients[2])
g3<- unname(full5$coefficients[3])
g4<- unname(full5$coefficients[4])
g5<- unname(summary(full5)$r.squared)
```

* `r g1`, `r g2`, `r g3`, `r g4` are the coefficients for pk, pj, numtree, and emission respectively.   
* `r g5` is the R squared for the new full model in Staten Island.


```{r,echo=FALSE,warning=FALSE,message=FALSE}
##grid plot of chinese coins

grid.newpage()
grid.circle(x=.2, y=4.7/6, r=0.2, gp=gpar(fill="tan4"))
grid.rect(x=.2, y=4.7/6, width=unit(0.1,"npc"), height = unit(0.1,"npc"))
grid.circle(x=.55, y=4.7/6, r=0.15, gp=gpar(fill="tan3"))
grid.rect(x=.55, y=4.7/6, width=unit(0.075,"npc"), height = unit(0.075,"npc"))
grid.circle(x=.8, y=4.7/6, r=0.1, gp=gpar(fill="tan2"))
grid.rect(x=.8, y=4.7/6, width=unit(0.05,"npc"), height = unit(0.05,"npc"))
grid.circle(x=.95, y=4.7/6, r=0.05, gp=gpar(fill="tan1"))
grid.rect(x=.95, y=4.7/6, width=unit(0.025,"npc"), height = unit(0.025,"npc"))
grid.text(x=.2, y=4.7/6, "$$$$$$")
grid.text(x=.55, y=4.7/6, "$$$$")
grid.text(x=.8, y=4.7/6, "$$$")
grid.text(x=.95, y=4.7/6, "$")
grid.text(x=.2, y=0.5, "pk")
grid.text(x=.55, y=0.5, "pj")
grid.text(x=.8, y=0.5, "numtree")
grid.text(x=.95, y=0.5, "emission")

```

*  The four coins of different sizes and colors represent the different influence of the four variables for housing prices.  


#**4 Conclusion**:  
  
  
Housing prices in NYC vary in a wide range. We choose the numbers of death and injury casued by car collisons, the total GMG emissions and the condition of trees to represent safety, pollution condition and vegetation coverages separately in these five boroughs. By analyzing thoroughly these datasets (including Total Number of Trees in 2015, Numbers of Deaths And Injuries Caused By Car Collision in 2015 and Total Greehhouse Gas (GHG) Emission in 2013). After constructing linear regression models using these three datasets and Housing Price In 2015 to give quantative interpretations, we finally found some models after numerous modifications.However, even though the R squared value is high, the constancy of errors is still a violation of the assumption of Linear Regression Model. In addition, the coefficients we found differ tremendously which is somewhat abnormal. Thus, we will conclude that the the linear regression model might not be a good model to use for our problem and these four datasets have no significant influence on the housing price of NYC compared with the other outstanding factors.  
    
    
    
    
    
    
      
      
#**5 References**: 
[1] Department of Parks and Recreation (DPR). (2017).  2015 Street Tree Census - Tree Data -- .[Data file].  Available from NYC OpenData Web site https://data.cityofnewyork.us/Environment/2015-Street-Tree-Census-Tree-Data/uvpi-gqnh

[2] NYPD. (2017). Vehicle Collisions in NYC, 2015-Present [Data file]. Available from Kaggle Web site
https://www.kaggle.com/nypd/vehicle-collisions

[3] Mayor's Office of Long Term Planning and Sustainability (OLTPS). (2017). Energy and Water Data Disclosure for Local Law 84 (2013)[Data file].  Available from NYC OpenData Web site 
https://data.cityofnewyork.us/Environment/Energy-and-Water-Data-Disclosure-for-Local-Law-84-/rgfe-8y2z

[4] Department of Finance (DOF).(2017). Annualized Rolling Sales Update. [Data file]. Available from NYC OpenData Web site https://data.cityofnewyork.us/Housing-Development/Annualized-Rolling-Sales-Update/uzf5-f8n2
